Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-21 papers/EMNLP2019/analysis.tex
moves table with modeling results.

\subsection{Variation: Specificity and Other Sources}
\label{ssec:variation}
Previous work on object naming has mostly adopted taxonomy-driven models aimed at capturing different levels of specificity (see Section \ref{sec:relwork}).
%This section shows that naming variation in ManyNames cannot be explained by this parameter.
This parameter does not explain the variation in ManyNames, as we will show in the following. 
Given that the \vg names are already linked to WordNet synsets, we compute the same linking for the additional ManyNames names, and examine whether they stand in a taxonomic relation to the objects'  \vg  synsets.
For detecting hypernyms, we use the hypernym closure of the synset with a depth of 10, the other relations are straightforward. 
% given by \vg.
%%In this section, we take a closer look at the lexical variation we observe in our data set. 
%We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}. These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
%For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),... \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ... w_n$ constitute the less frequent alternatives of $w_{top}$.  The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs. The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
%In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
%The naming variants can be grouped according to their lexical relation, as follows:
%
%\begin{itemize}
%\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
%\item \textbf{hyponymy}: e.g.\ man vs. person
%\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
%\item \textbf{no relation}: e.g.\  desk vs. apple
%\end{itemize}
%\cs{Shouldn't we mention that we consider only simple move-up hypernymy relations?}
Table \ref{tab:rel} shows the distribution
how frequently names with a certain relation to the synset occur in the ManyNames responses, in terms of their  type and token frequency. 
%\cs{something went wrong here --- "(?)Table\ \ref{tab:rel} shows the relative frequency distribution of the relations (between the MN names %types and tokens, respectively, 
%and the VG synsets) in the aggregated class-level response sets." // "Table \ref{tab:rel} shows the relative frequency distribution of the different relations which occur between the MN names and the VG synsets in the aggregated class-level response sets."} 
%\gbt{what do you mean, `` aggregated class-level response set''?}
%\cs{Considering the track we are submitting to, one or two examples per relation in an additional column in the table wouldn't hurt.}
The coverage of WordNet for our name data is satisfactory (90\%\ of the name types, accounting for 97\%\ of the tokens).
Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.
However, in the vast majority of cases no hierarchical relation between the name and the synset can be retrieved from WordNet.
Thus, strikingly, most of the naming variation in ManyNames is \textit{not} related to different preferences in levels of specificity, %\cs{(as far as it can be determined using WordNet)}
 but to other sources. The following qualitative analysis discusses other types of variation in the data, illustrated with examples in Figure\ \ref{fig:ex-high-low-agreement}:

\begin{table}
\small
\centering
\setlength{\tabcolsep}{2pt}
\begin{tabular}{lcc|p{2.5cm}}
\toprule
         relation & \% types & \% token & \it ex: jacket \\
\midrule
% meronym &  0.1 &  0.2 \\
% holonym &  0.1 &  0.4 \\
 word-not-covered &  10.6 &  2.6 & \it outdoor vest\\
\midrule
 synonym &  1.1 &  1.1 & \it hoodie  \\
 hyponym &  2.2 &  3.8 & \it parka, blazer \\
 co-hyponym &  3.1 &  5.9 & \it raincoat\\
 hypernym &  10.5 &  27.7 & \it clothing, coat\\
 rel-not-covered &  72.2 &  58.3 & \it sweatshirt, man\\
\bottomrule
\end{tabular}
\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets.}
\label{tab:rel}
\vspace{-0.5cm}
\end{table}

@@

Our ManyNames dataset provides a means 
(i) to study how different people would name the same object (image region) \cs{"visual awareness" would fit in here}, and, given a specific name, estimate its degree of preference, which might vary substantially across different instances of a class, and   
%assess the extent to which different speakers prefer that name, which might vary substantially across different instances of a class, and to 
(ii) to obtain a set of possible names for individual objects, as well as available lexical alternatives for specific names, which again might vary strongly across instances and often cannot be retrieved from existing taxonomies like WordNet.

@@

>>>>

\subsection{Variation: Specificity and Other Sources}
\label{ssec:variation}
Previous work on object naming has mostly adopted taxonomy-driven models aimed at capturing different levels of specificity (see Section \ref{sec:relwork}).
%This section shows that naming variation in ManyNames cannot be explained by this parameter.
This parameter does not explain the variation in ManyNames, as we will show in the following. 
Given that the \vg names are already linked to WordNet synsets, we compute the same linking for the additional ManyNames names, and examine whether they stand in a taxonomic relation to the objects'  \vg  synsets.
For detecting hypernyms, we use the hypernym closure of the synset with a depth of 10, the other relations are straightforward. 
% given by \vg.
%%In this section, we take a closer look at the lexical variation we observe in our data set. 
%We analyze the data points where participants attributed different names to the same object and extract a set of  pairwise \textbf{naming variants}. These naming variants correspond to pairs of words that can be used interchangeably to name certain objects.
%For each object, we extract the set of naming variants $s = \{ (w_{top},w_2), (w_{top},w_3), (w_{top},w_4),... \}$  where $w_{top}$ is the most frequent name annotated for the object and $w_2 ... w_n$ constitute the less frequent alternatives of $w_{top}$.  The  \textbf{type frequency} of a naming variant $(w_{top},w_x)$ corresponds to the number of objects where this variant occurs. The \textbf{token frequency} of $(w_{top},w_x)$ corresponds the count of all annotations where $w_x$ has been used instead of $w_{top}$.
%In Table \ref{tab:exvariants}, we show the naming variants with the highest raw token frequency for each domain. 
%The naming variants can be grouped according to their lexical relation, as follows:
%\begin{itemize}
%\item \textbf{synonymy}: e.g.\ aircraft vs. airplane 
%\item \textbf{hyponymy}: e.g.\ man vs. person
%\item \textbf{co-hyponymy}: e.g.\ swan vs. goose
%\item \textbf{no relation}: e.g.\  desk vs. apple
%\end{itemize}
%\cs{Shouldn't we mention that we consider only simple move-up hypernymy relations?}
Table \ref{tab:rel} shows the distribution
how frequently names with a certain relation to the synset occur in the ManyNames responses, in terms of their  type and token frequency. 
%\cs{something went wrong here --- "(?)Table\ \ref{tab:rel} shows the relative frequency distribution of the relations (between the MN names %types and tokens, respectively, 
%and the VG synsets) in the aggregated class-level response sets." // "Table \ref{tab:rel} shows the relative frequency distribution of the different relations which occur between the MN names and the VG synsets in the aggregated class-level response sets."} 
%\gbt{what do you mean, `` aggregated class-level response set''?}
%\cs{Considering the track we are submitting to, one or two examples per relation in an additional column in the table wouldn't hurt.}
The coverage of WordNet for our name data is satisfactory (90\%\ of the name types, accounting for 97\%\ of the tokens).
Among the names that do have a hierarchical relation to the synset, hypernyms are the most frequent, meaning that our annotators often went for a more general name than the \vg annotators.
However, in the vast majority of cases no hierarchical relation between the name and the synset can be retrieved from WordNet.
Thus, strikingly, most of the naming variation in ManyNames is \textit{not} related to different preferences in levels of specificity, %\cs{(as far as it can be determined using WordNet)}
 but to other sources. The following qualitative analysis discusses other types of variation in the data, illustrated with examples in Figure\ \ref{fig:ex-high-low-agreement}:
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{2pt}
\begin{tabular}{lcc|p{2.5cm}}
\toprule
         relation & \% types & \% token & \it ex: jacket \\
\midrule
% meronym &  0.1 &  0.2 \\
% holonym &  0.1 &  0.4 \\
 word-not-covered &  10.6 &  2.6 & \it outdoor vest\\
\midrule
 synonym &  1.1 &  1.1 & \it hoodie  \\
 hyponym &  2.2 &  3.8 & \it parka, blazer \\
 co-hyponym &  3.1 &  5.9 & \it raincoat\\
 hypernym &  10.5 &  27.7 & \it clothing, coat\\
 rel-not-covered &  72.2 &  58.3 & \it sweatshirt, man\\
\bottomrule
\end{tabular}
\caption{Lexical relations of naming variants in ManyNames to annotated \vg synset, averaged over synsets.}
\label{tab:rel}
\vspace{-0.5cm}
\end{table}

@@

Our ManyNames dataset provides a means 
(i) to study how different people would name the same object (image region),  
%\cs{"visual awareness" would fit in here}, 
and, given a specific name, estimate its degree of preference, which might vary substantially across different instances of a class, and   
%assess the extent to which different speakers prefer that name, which might vary substantially across different instances of a class, and to 
(ii) to obtain a set of possible names for individual objects, as well as available lexical alternatives for specific names, which again might vary strongly across instances and often cannot be retrieved from existing taxonomies like WordNet.

@@

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr@{~}|@{~}r@{~}r@{~}rr}
		\toprule
		%{} &  All images-top=VG &  All images-top=MN &  All images-top\$\textbackslash in\$MN &  All images-KL &  VGnotMN-top=VG &  VGnotMN-top=MN &  VGnotMN-top\$\textbackslash in\$MN &  VGnotMN-KL &  notTrain-top=VG &  notTrain-top=MN &  notTrain-top\$\textbackslash in\$MN &  notTrain-KL \\
		& \multicolumn{12}{c}{Image subset} \\
		&	\multicolumn{4}{c}{All ($24,585$)} 
		& \multicolumn{4}{c}{VG$\neq$MN ($6,280$)}
		& \multicolumn{4}{c}{$\neg$Training ($2,281$)} \\
		\midrule
		&  \multicolumn{2}{c}{single-label}
		&  \multicolumn{2}{c}{multi-label}
		&  \multicolumn{2}{c}{single-label}
		&  \multicolumn{2}{c}{multi-label}
		&  \multicolumn{2}{c}{single-label}
		&  \multicolumn{2}{c}{multi-label} \\
		Domain	 &  =VG & =MN & $\in$MN  &  KL
		&  =VG & =MN & $\in$MN  & KL
		&  =VG & =MN & $\in$MN  & KL\\ 
		\midrule \vspace{.6ex}
		all            &               68.7 &                 76.8 &                   94.8 &            0.9 &            20.7 &              52.6 &                92.4 &         1.2 &             63.5 &               73.1 &                 92.5 &          1.0 \\ 
		home           &               70.0 &                 74.7 &                   93.4 &            1.1 &            24.3 &              47.5 &                91.4 &         1.4 &             67.2 &               70.5 &                 92.5 &          1.2 \\
		food           &               60.0 &                 71.9 &                   87.7 &            1.0 &            14.2 &              48.9 &                76.6 &         1.5 &             46.6 &               62.1 &                 80.1 &          1.3 \\
		buildings      &               57.5 &                 70.7 &                   92.1 &            1.3 &             7.9 &              63.4 &                89.8 &         1.5 &             44.3 &               60.2 &                 88.6 &          1.4 \\
		vehicles       &               69.8 &                 72.8 &                   97.6 &            0.6 &            35.3 &              46.1 &                97.4 &         0.7 &             67.2 &               73.5 &                 96.4 &          0.7 \\
		animals/plants &               92.7 &                 94.8 &                   97.7 &            0.4 &            20.3 &              65.0 &                94.0 &         0.9 &             91.3 &               92.6 &                 96.2 &          0.5 \\
		clothing       &               63.3 &                 70.9 &                   92.6 &            1.0 &            19.9 &              48.5 &                90.3 &         1.2 &             50.8 &               60.2 &                 87.4 &          1.3 \\
		people         &               48.5 &                 70.7 &                   95.5 &            1.2 &            13.8 &              58.9 &                95.3 &         1.3 &             42.2 &               68.2 &                 92.8 &          1.2 \\
		\bottomrule
		%Baseline      &                3.3 &                  5.2 &                   12.0 &            -- &             1.7 &               9.3 &                21.8 &         -- &              3.0 &                5.0 &                 11.9 &          -- \\
		Baseline       &                3.9 &                  4.6 &                    5.6 &            -- &             0.1 &               3.0 &                 3.8 &         -- &              3.8 &                4.6 &                  5.8 &          -- \\
	\end{tabular}
	\caption{Baseline: The most frequent name. Random baseline (KL with random distributions) for each image set: 6.9 (all), 6.5 (VG$\neq$MN) and 6.9 ($\neg$Training). The numbers in parentheses give the \# instances in each set.	\label{tab:model}}
\end{table*}

### 2019-05-21 papers/EMNLP2019/conclusion.tex

The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.
For modeling, it provides data on possible names for objects that constitutes a more robust testing ground.
In future work, we want to use the ManyNames data to fine-tune existing models such that their behavior is more human-like, and check if models trained on the ManyNames data perform better than models trained on single labels. \gbt{@Carina, pls check if this is what you meant}

For theoretical work, it provides name variation data with natural images and thus at the \textit{instance} level, as opposed to the category level that has been the focus up to now in theoretical work, due to the use of highly stylized drawings.
This affords tremendous opportunities to study factors affecting object naming that have not been studied to date, such as prototypicality of the instance itself, or the effect of the visual context.
However, it also comes with its own challenges, the main one being the issue of object identification, that we have found to interfere with the study of true naming variation.
Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between true mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag} when the two overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).
This of course is not an issue when working with the kind of images that traditional studies in Psycholinguistics have used, and future work will need to address it.
\gbt{Do you think this is too negative as a conclusion? I feel like it's the elephant in the room -- if we don't say it here, we should say it somewhere prominently.}

>>>>

The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.
For modeling, it provides data on possible names for objects that constitutes a more robust testing ground.
%In future work, we want to use the ManyNames data to fine-tune  existing models tsuch that their behavior is more human-like, and check if models trained on the ManyNames data perform better than models trained on single labels. \gbt{@Carina, pls check if this is what you meant}
In future work, we want to use ManyNames to fine-tune and examine  existing models in a multi-label setting towards a behavior that is more human-like. 
%, and check if models trained on the ManyNames data perform better than models trained on single labels. \gbt{@Carina, pls check if this is what you meant}

For theoretical work, it provides name variation data with natural images and thus at the \textit{instance} level, as opposed to the category level that has been the focus up to now in theoretical work, due to the use of highly stylized drawings.
This affords tremendous opportunities to study factors affecting object naming that have not been studied to date, such as prototypicality of the instance itself, or the effect of the visual context.

%However, it also comes with its own challenges, the main one being the issue of object identification, that we have found to interfere with the study of true naming variation. 
The use of naturalistic images in place of stylized drawings also comes with new challenges, which interfere with the study of naming variation: the factors inherently underlying variations cannot be easily separated from those introduced by issues such as object identification.  
Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between true mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag} when the two overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).
%This of course is not an issue when working with the kind of images that traditional studies in Psycholinguistics have used, and future work will need to address this.
Future work will need to address these challenges. 
\gbt{Do you think this is too negative as a conclusion? I feel like it's the elephant in the room -- if we don't say it here, we should say it somewhere prominently.}

### 2019-05-21 papers/EMNLP2019/suppl_material.tex

Figures~\ref{fig:instructions1} and~\ref{fig:instructions2} contain the instructions for our subjects in the first round and rounds 2-4, respectively.
After the first round, based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection). This yielded $25,596$ images, discarding $5,497$.

\begin{itemize}
\item they were not marked as occluded by any subject;
\item ``Bounding box is unclear'' was marked at most twice;
\item at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects);
\item the most frequent elicited name is of the same domain as the \vgenome name.
\end{itemize}

Table~\ref{tab:overview_dataset2} gives an overview of the collection synsets, XXX, XXX, grouped into the $7$~domains.
\gbt{@Carina, the table doesn't fit, maybe put one domain x row?}

\begin{table*}[htb]
\small
	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
	\toprule
	        animals\_plants &               vehicles &                        home &                clothing &                   buildings &                    food &                 people \\
	\midrule
	  ungulate$_1$ (2037) &  aircraft$_1$ (1208) &  furnishing$_2$ (5355) &  shirt$_1$ (968) &  house$_1$ (364) &  dish$_2$ (812) &  woman$_1$ (1768) \\
	 horse$_1$ (833) &  train$_1$ (957) &  vessel$_3$ (525) &  overgarment$_1$ (786) &  bridge$_1$ (297) &  baked\_goods$_1$ (770) &  man$_1$ (1167) \\
	  feline$_1$ (763) &  car$_1$ (727) &  kitchen\_utensil$_1$ (132) &  dress$_1$ (199) &  shelter$_1$ (169) &  foodstuff$_2$ (280) &  male\_child$_1$ (853) \\
	 dog$_1$ (688) &  motorcycle$_1$ (564) &  crockery$_1$ (92) &  headdress$_1$ (135) &  restaurant$_1$ (58) &  vegetable$_1$ (48) &  athlete$_1$ (396) \\
	  bird$_1$ (389) &  truck$_1$ (559) &  cutlery$_2$ (82) &  neckwear$_1$ (65) &  outbuilding$_1$ (31) &  edible\_fruit$_1$ (42) &  child$_1$ (333) \\
	  flower$_1$ (44) &  boat$_1$ (499) &  tool$_1$ (72) &  robe$_1$ (27) &  hotel$_1$ (19) &  beverage$_1$ (23) &  creator$_2$ (11) \\
	  rodent$_1$ (27) &  ship$_1$ (38) &  lamp$_1$ (34) &  glove$_2$ (7) &  housing$_1$ (17) &   &  professional$_1$ (5) \\
	 insect$_1$ (12) &   &   &  footwear$_1$ (5) &  place\_of\_worship$_1$ (12) &   &   \\
	  fish$_1$ (11) &   &   &   &   &   &   \\
	\bottomrule
\end{tabular}
	\caption{Overview of our dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset2}}
      \end{table*}

@@

\begin{table*}
	\small
	\centering
\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
	\toprule
	          vehicles &            food & animals\_plants &           home &        buildings &             people &      clothing \\
	\midrule
	  train (954) &  pizza (518) &  giraffe (915) &  bed (888) &  house (340) &  boy (853) &  shirt (904) \\
	  car (642) &  cake (261) &  horse (822) &  bench (714) &  bridge (274) &  man (806) &  jacket (451) \\
	  plane (485) &  bread (186) &  cat (754) &  table (687) &  dugout (91) &  woman (766) &  coat (267) \\
	  airplane (479) &  sandwich (153) &  dog (654) &  desk (672) &  tent (53) &  girl (650) &  dress (190) \\
	  motorcycle (466) &  bun (143) &  zebra (461) &  counter (516) &  restaurant (33) &  lady (342) &  hat (77) \\
	  truck (465) &  cheese (110) &  cow (324) &  couch (366) &  overpass (23) &  guy (330) &  t-shirt (62) \\
	 boat (450) &  donut (78) &  bird (295) &  chair (365) &  grill (22) &  child (230) &  tie (51) \\
	  jet (106) &  salad (70) &  sheep (216) &  carpet (307) &  garage (18) &  batter (110) &  blazer (43) \\
	  aircraft (85) &  sauce (68) &  bull (48) &  bowl (219) &  hotel (16) &  kid (85) &  hood (26) \\
	  van (76) &  apple (33) &  flower (40) &  curtain (182) &  castle (14) &  skateboarder (80) &  cap (20) \\
	\bottomrule
\end{tabular}
	\caption{Overview of our ManyNames dataset: Top-10 VG names for each domain (number of instances in parentheses). \textbf{double-check} \label{tab:overview_dataset1}}
\end{table*}

>>>>

Figures~\ref{fig:instructions1} and~\ref{fig:instructions2} contain the instructions for our subjects in the first round and rounds 2-4, respectively.
After the first round, based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection):
\begin{itemize}
\item they were not marked as occluded by any subject;
\item ``Bounding box is unclear'' was marked at most twice;
\item at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects);
\item the most frequent elicited name is of the same domain as the \vgenome name.
\end{itemize}
This yielded $25,596$ images, discarding $5,497$.
Table~\ref{tab:overview_dataset1} shows the $7$\ domains together with the top $10$\ VG names.

Table~\ref{tab:overview_dataset2} gives an overview of the collection synsets, grouped into the $7$~domains.
\gbt{@Carina, the table doesn't fit, maybe put one domain x row?}

\begin{table*}[htb]
\small
	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
	\toprule
	        animals\_plants &               vehicles &                        home &                clothing &                   buildings &                    food &                 people \\
	\midrule
	  ungulate$_1$ (2037) &  aircraft$_1$ (1208) &  furnishing$_2$ (5355) &  shirt$_1$ (968) &  house$_1$ (364) &  dish$_2$ (812) &  woman$_1$ (1768) \\
	 horse$_1$ (833) &  train$_1$ (957) &  vessel$_3$ (525) &  overgarment$_1$ (786) &  bridge$_1$ (297) &  baked\_goods$_1$ (770) &  man$_1$ (1167) \\
	  feline$_1$ (763) &  car$_1$ (727) &  kitchen\_utensil$_1$ (132) &  dress$_1$ (199) &  shelter$_1$ (169) &  foodstuff$_2$ (280) &  male\_child$_1$ (853) \\
	 dog$_1$ (688) &  motorcycle$_1$ (564) &  crockery$_1$ (92) &  headdress$_1$ (135) &  restaurant$_1$ (58) &  vegetable$_1$ (48) &  athlete$_1$ (396) \\
	  bird$_1$ (389) &  truck$_1$ (559) &  cutlery$_2$ (82) &  neckwear$_1$ (65) &  outbuilding$_1$ (31) &  edible\_fruit$_1$ (42) &  child$_1$ (333) \\
	  flower$_1$ (44) &  boat$_1$ (499) &  tool$_1$ (72) &  robe$_1$ (27) &  hotel$_1$ (19) &  beverage$_1$ (23) &  creator$_2$ (11) \\
	  rodent$_1$ (27) &  ship$_1$ (38) &  lamp$_1$ (34) &  glove$_2$ (7) &  housing$_1$ (17) &   &  professional$_1$ (5) \\
	 insect$_1$ (12) &   &   &  footwear$_1$ (5) &  place\_of\_worship$_1$ (12) &   &   \\
	  fish$_1$ (11) &   &   &   &   &   &   \\
	\bottomrule
\end{tabular}
	\caption{Overview of our dataset: Synset nodes for each domain (subscript indicates synset number; number of instances in parentheses). %\textbf{double-check}
		 \label{tab:overview_dataset2}}
      \end{table*}

@@

\begin{table*}
	\small
	\centering
\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
	\toprule
	          vehicles &            food & animals\_plants &           home &        buildings &             people &      clothing \\
	\midrule
	  train (954) &  pizza (518) &  giraffe (915) &  bed (888) &  house (340) &  boy (853) &  shirt (904) \\
	  car (642) &  cake (261) &  horse (822) &  bench (714) &  bridge (274) &  man (806) &  jacket (451) \\
	  plane (485) &  bread (186) &  cat (754) &  table (687) &  dugout (91) &  woman (766) &  coat (267) \\
	  airplane (479) &  sandwich (153) &  dog (654) &  desk (672) &  tent (53) &  girl (650) &  dress (190) \\
	  motorcycle (466) &  bun (143) &  zebra (461) &  counter (516) &  restaurant (33) &  lady (342) &  hat (77) \\
	  truck (465) &  cheese (110) &  cow (324) &  couch (366) &  overpass (23) &  guy (330) &  t-shirt (62) \\
	 boat (450) &  donut (78) &  bird (295) &  chair (365) &  grill (22) &  child (230) &  tie (51) \\
	  jet (106) &  salad (70) &  sheep (216) &  carpet (307) &  garage (18) &  batter (110) &  blazer (43) \\
	  aircraft (85) &  sauce (68) &  bull (48) &  bowl (219) &  hotel (16) &  kid (85) &  hood (26) \\
	  van (76) &  apple (33) &  flower (40) &  curtain (182) &  castle (14) &  skateboarder (80) &  cap (20) \\
	\bottomrule
\end{tabular}
	\caption{Overview of our ManyNames dataset: Top-10 VG names for each domain (number of instances in parentheses). %\textbf{double-check}
		 \label{tab:overview_dataset1}}
\end{table*}
